---
title: "Zane's `R` Coding Exercise"
output: 
  html_document:
    toc: FALSE
editor_options:
  chunk_output_type: console
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(include = TRUE, echo = TRUE)
```

For this exercise, I want to work on the `gapminder` data from the `dslabs` package. First, I want to get an idea of what this dataset looks like.

```{r importing data}
# The dslabs package is where the data we want to use lives.
library(dslabs)

# We also need the tidyverse package for analysis later.
library(tidyverse)

# Use the scales package to make plot labels nicer
library(scales)

# Use the brooms package to help move data into easier format for tables
library(broom)

#Allows for easy to create tables from statistical data
library(knitr)
library(kableExtra)

# Open the help file for the gapminder data to examine contents.
help(gapminder)

# Examine the structure of the gapminder data
str(gapminder)

# Get a summary of the gapminder data variables
summary(gapminder)

# Print the class of the gapminder object
class(gapminder)
```

For this exercise, I am only interested in the data from countries in Africa.

```{r filtering rows}
# Filter out records where the continent is "Africa"
africadata <- gapminder %>%
  dplyr::filter(continent == "Africa")

# View structure and summary of the Africa-only data to see what changed.
str(africadata)
summary(africadata)
```

The two relationships I am interested in are:
* infant mortality and life expectancy, and
* population and life expectancy.

```{r selecting columns}
# Create a data frame with only infant mortality and life expectancy
africa_im_le <- africadata %>%
  dplyr::select(infant_mortality, life_expectancy)

str(africa_im_le)
summary(africa_im_le)

# Create a data frame with only population size and life expectancy
africa_ps_le <- africadata %>%
  dplyr::select(population, life_expectancy)

str(africa_ps_le)
summary(africa_ps_le)
```

Next I will visualize these two relationships.

```{r plotting}
# scatterplot of life expectancy vs infant mortality
africa_im_le %>%
  # define which fields to plot
  ggplot(aes(x = infant_mortality, y = life_expectancy)) +
  # make the plot a scatterplot
  geom_point() +
  # change the way the plot looks (i.e. changing "non-data ink")
  theme_bw() +
  # make the axis titles nicer
  labs(
    x = "Infant mortality (deaths per 1000)",
    y = "Life expectancy (years)"
  )

# scatterplot of life expectancy vs population size
africa_ps_le %>%
  # define which fields to plot
  ggplot(aes(x = population, y = life_expectancy)) +
  # make the plot a scatterplot
  geom_point() +
  # change the way the plot looks
  theme_bw() +
  # Make the axis titles nicer
  labs(
    x = "Population",
    y = "Life expectancy (years)"
  ) +
  # customize the x-axis scale
  scale_x_continuous(
    # use a log scale for population size
    trans = "log10",
    # format the values with commas rather than scientific notation
    labels = scales::comma
  )
```

Uh-oh! We can see that due to the inclusion of multiple years for each country, there is clearly autocorrelation and this makes the graphs look quite weird. We also got an error about missing data, with more data points missing for life expectancy.

Now I only want to plot one year at a time, so I will combine this with the missing data. First, I can find which years have missing data, and then I can choose a year to plot which does not have (or has the least amount of) missing values.

```{r missing data processing}
africadata %>%
  # Filter for any rows where either variable is NA (missing)
  dplyr::filter(is.na(infant_mortality) | is.na(life_expectancy)) %>%
  # Count up the number of missing records for each year
  dplyr::count(year, sort = TRUE, name = "# records missing")
```

It appears that for either of these two fields, there are missing records in 2016, and for years from 1961 through 1981. I will use the year 2000 for the next plot.

```{r filter 2000}
# Filter only records where the year is 2000
africadata_2000 <- africadata %>%
  filter(year == 2000)

# Check to see if everything worked alright
str(africadata_2000)
summary(africadata_2000)
```

Now I can remake the plots using only the data from the year 2000, solving both plotting problems at the same time.

```{r plotting 2000 only}
# scatterplot of life expectancy vs infant mortality
africadata_2000 %>%
  # define which fields to plot
  ggplot(aes(x = infant_mortality, y = life_expectancy)) +
  # make the plot a scatterplot
  geom_point() +
  # change the way the plot looks (i.e. changing "non-data ink")
  theme_bw() +
  # make the axis titles nicer
  labs(
    x = "Infant mortality (deaths per 1000)",
    y = "Life expectancy (years)"
  )

# scatterplot of life expectancy vs population size
africadata_2000 %>%
  # define which fields to plot
  ggplot(aes(x = population, y = life_expectancy)) +
  # make the plot a scatterplot
  geom_point() +
  # change the way the plot looks
  theme_bw() +
  # Make the axis titles nicer
  labs(
    x = "Population",
    y = "Life expectancy (years)"
  ) +
  # customize the x-axis scale
  scale_x_continuous(
    # use a log scale for population size
    trans = "log10",
    # format the values with commas rather than scientific notation
    labels = scales::comma
  )
```

Now we have a good idea what the relationships look like: I expect a negative linear relationship between life expectancy and infant mortality, and no relationship between life expectancy and population.

I will fit a simple linear model to test both of these predictions.

```{r linear model}
# Fit both of the simple linear models
fit1 <- lm(life_expectancy ~ infant_mortality, data = africadata_2000)
fit2 <- lm(life_expectancy ~ population, data = africadata_2000)

# Get information about both of the models
summary(fit1)
summary(fit2)
```

From the first model (with infant mortality as the predictor), I obtain an estimated slope of about `r round(coef(fit1)[[2]], 2)` (*p* < 0.001). Thus, I conclude that for African countries in the year 2000, an increase of 1 infant death out of every 1000 births was associated with a decrease of `r round(abs(coef(fit1)[[2]]), 2)` years in life expectancy (about `r round(coef(fit1)[[2]], 2) * 12` months).

From the second model (with population size as the predictor), I obtained a very very small slope which rounds to 0 unless I use an unreasonable amount of precision. Since the *p*-value is also quite large (*p* = `r round(summary(fit2)$coefficients[[2, 4]], 4)`), I think it is reasonable to conclude that there was no (linear) relationship between life expectancy and population size for African countries in the year 2000.

# Part 2

Now that we have examined if a correlation exists between life expectancy and population and life expectancy and infant mortality, let us now analyze GDP and life expectancy and GDP and population with the data from African countries in the year 2000 to determine if there exists a relationship.

```{r, warning= F}
africadata_2000 %>%
  ggplot(aes(x=life_expectancy, y=gdp))+
  geom_point()+
  ggtitle("Comparison of life expectancy and gdp in Africa")+
xlab("life expectancy")+
  scale_x_continuous(name="life expectancy", labels = comma) +
  ylab("gdp")
```

It appears as though there is no correlation between life expectancy and GDP. We will now examine if there is a relationship between population and GDP.

```{r, warning= F}
africadata_2000 %>%
  ggplot(aes(x=population, y=gdp))+
  geom_point()+
  ggtitle("Comparison of Life Expectancy and Population Size in Africa")+
xlab("Population")+
  scale_x_continuous(name="Population", labels = comma)+
  ylab("GDP")+
  scale_y_continuous(name="GDP", labels = comma)
```

It appears as though there is correlation between population size and GDP, as greater population size has the effect of increasing GDP. 

**The last step we will do is to utilize linear regression models to compare the two plots for any link, note that we will use fit3 and fit4, as fit1 and 2 have already been used.**

```{r}
fit3 <-lm(gdp ~ life_expectancy, data=africadata_2000)
fit4 <-lm(gdp ~ population, data = africadata_2000)
```

**Now we summarize our models**
```{r}
summary(fit3)
summary(fit4)
```

Because the final p-value of the third model is 0.0152, which is less than 0.05, we can conclude that there **does** exist a positive correlation between life expectancy and gdp.

Because the final p-value of the fourth model is 1.186e-05, which is less than 0.-05, we can conclude that there is a substantial correlation between population and gdp.

Next, we will create a multiple linear regression model using gdp as the outcome and both life expectancy and population size as independent variables, which will allow us to examine further the strenghts of these relationships between variables. We will then utiliae a table for easy to understand output. 
**Note that we will call this new model fit5**

```{r}
fit5 <-lm(gdp ~ life_expectancy + population, data = africadata_2000)

##We will then summarize the output
summary(fit5)
```

Finally we need to create an easy to understand table

```{r}
fit5%>%
tidy() %>%
kbl() %>%
kable_material_dark("hover", full_width=F, html_font='times')
```

Therefore, we can conclude that with a p-value of <0.05, there is significance between GDP, life expectancy, and population. If the p-value is lowered to be even more specific at <0.01, there still exists a statistically significant relationship between gdp and life expectancy adjusting for population size. 